Applications of Technology and Large Data in Statistics Education and Statistical Graphics

### 2015-05-25 DefenseSlides/DefenseSlidesCommitteeHour.Rnw
m
remove Dropbox directory reference

<<Stripes, echo=FALSE, warning=FALSE, fig.width=7, fig.height=3.5, out.width='.99\\linewidth', fig.pos='h',fig.align='center',fig.show='hold'>>=
setwd("C:\\Users\\Karsten\\Documents\\GitHub\\dbaccess")
allbindat <- read.csv("StripeBinData.csv",header=TRUE)
allbindat$BinningType <- factor(allbindat$BinningType, levels=c("Standard","Random"))

@@

<<OriginShiftCoarse, echo=FALSE, warning=FALSE, fig.width=7, fig.height=3.5, out.width='.99\\linewidth', fig.pos='h',fig.align='center',fig.show='hold'>>=
library(plyr)
setwd("C:\\Users\\Karsten\\Documents\\GitHub\\dbaccess")
lossOrigin <- read.csv("LossesByOriginBinwidth.csv",header=TRUE)
lossOrigin$binsize <- factor(paste(lossOrigin$widthx,"X",lossOrigin$widthx,sep=""),
                             levels=c("2X2","4X4","6X6","8X8","10X10"))

@@

\begin{frame}
    \frametitle{Software Development}    
  Goals
    \begin{itemize}
      \item Connect intro students with big data
      \item Bypass technical hurdles of big data
    \end{itemize} \pause
  Technical Components
    \begin{itemize}
      \item \textit{Data storage}: MySQL
      \item \textit{Computation}: \texttt{R}, \texttt{shiny}, \texttt{RMySQL}
      \item \textit{User interface}: accessed through web browser
    \end{itemize} \pause
  Interface Design
    \begin{itemize}
      \item Quality characteristics of software design
      \item Cognitive load theory
      \item Human centered design
      \item Pedagogical value and curricular integration
    \end{itemize}
\end{frame}

>>>>

<<Stripes, echo=FALSE, warning=FALSE, fig.width=7, fig.height=3.5, out.width='.99\\linewidth', fig.pos='h',fig.align='center',fig.show='hold'>>=
# setwd("C:\\Users\\Karsten\\Documents\\GitHub\\dbaccess")
allbindat <- read.csv("Data/StripeBinData.csv",header=TRUE)
allbindat$BinningType <- factor(allbindat$BinningType, levels=c("Standard","Random"))

@@

<<OriginShiftCoarse, echo=FALSE, warning=FALSE, fig.width=7, fig.height=3.5, out.width='.99\\linewidth', fig.pos='h',fig.align='center',fig.show='hold'>>=
library(plyr)
# setwd("C:\\Users\\Karsten\\Documents\\GitHub\\dbaccess")
lossOrigin <- read.csv("Data/LossesByOriginBinwidth.csv",header=TRUE)
lossOrigin$binsize <- factor(paste(lossOrigin$widthx,"X",lossOrigin$widthx,sep=""),
                             levels=c("2X2","4X4","6X6","8X8","10X10"))

@@

\begin{frame}
    \frametitle{Shiny Database Sampler}    
  Goals
    \begin{itemize}
      \item Connect intro students with big data
      \item Bypass technical hurdles of big data
    \end{itemize} \pause
  Technical Components
    \begin{itemize}
      \item \textit{Data storage}: MySQL
      \item \textit{Computation}: \texttt{R}, \texttt{shiny}, \texttt{RMySQL}
      \item \textit{User interface}: accessed through web browser
    \end{itemize} \pause
  Interface Design
    \begin{itemize}
      \item Quality characteristics of software design
      \item Cognitive load theory
      \item Human centered design
      \item Pedagogical value and curricular integration
    \end{itemize}
\end{frame}
